---
title: "Homework 3"
author: "Jong Hyun Choi"
date: "3/7/2021"
output:
  word_document: default
  html_document: default
---

Problem 5.6 
Using the equation, C'= [N(N + 2)/4] − C
We know that N=m+n=40 and C = 185.5 given from the textbook 
```{r}
Capos = 40*(40+2)/4 - 185.5
Capos
```

Problem 5.7 
If we take an example and set n=3 and m=4, then our N=7. 
calculating the smallest C value would be 1+2+1, and the largest would be (N+1)/2 + (N-1)/2 +(N-2)/2
If we take an example and set n = 4 and m=4, then our N=8 
Calculating the smallest C value would be 1+2+2+1, and our largest would be (N/2) + (N/2) +(N-1)/2 (N-1)/2


Problem 5.9 
We want to use Wilcoxon test when we want to test the difference in the location, whereas the Ansari-Bradley tests the difference in their dispersions. Because these two tests are for different distribuions, so the result does not imply Ansari-Bradley

We do not reject the null hypothesis because our p-value is greater than 0.05
```{r}
set.seed(1)
x<−c(1042, 1617, 1180, 973, 1552, 1251, 1151, 1511, 728, 1079, 951, 1319) 
y<−c(874, 389, 612, 798, 1152, 893, 541, 741, 1064, 862, 213) 
ansari.test(x,y, exact = FALSE)
```



Problem 5.31 
We see that our p-value is less than 0.05 significance level. 
Therefore we reject the null hypothesis that there is no difference in location and no difference in variance between the control and SST data. 
Because example 4.2 told us about location by rejecting the null hypothesis and problem 9 told us about variance by not rejecting the null hypothesis, we can see that in Lepage where we test if two groups differ in dispersion or/and location, we reject the null hypothesis
```{r}
require(NSM3)
set.seed(1)
x<−c(1042, 1617, 1180, 973, 1552, 1251, 1151, 1511, 728, 1079, 951, 1319)
y<−c(874, 389, 612, 798, 1152, 893, 541, 741, 1064, 862, 213)
pLepage(x,y)
```


Problem 5.34
We can see that the p-value is less than 0.05 significance level. 
Therefore, we can reject the null hypothesis that there is no difference between the control and SST probability distribution.
Because there were difference in location, difference either in dispersion or/and location, we can see that in Kolmogorov-Smirnov test, we would see any general difference between 2 groups
```{r}
set.seed(1) 
x<−c(1042, 1617, 1180, 973, 1552, 1251, 1151, 1511, 728, 1079, 951, 1319)
y<−c(874, 389, 612, 798, 1152, 893, 541, 741, 1064, 862, 213)
ks.test(x,y)
```


Problem 8.3
Ho: τ=0 
H1: τ=/0
We see that our p-value is greater than 0.1 significance level. Therefore we do not reject the null hypothesis of independence between the brain weight and large fiber count. 
```{r}
data8.4=read.csv("tab8_4.csv")
```

```{r}
x= data8.4$weight
y= data8.4$count
cor.test(x,y, method = "kendall")
```


Problem 8.22
We can see that our tauhat is 0.2727273, which is the same tau that we got in our cor.test function in our previous question
```{r}
x= data8.4$weight
y= data8.4$count 
n = 11 
Qmat = matrix(0, n-1, n-1)  
colnames(Qmat) =1:(n-1) 
rownames(Qmat) = 2:n
for(i in 1:(n-1)){
  for(j in (i+1):n){
    qval=(y[j]-y[i])*(x[j]-x[i])
    if(qval>0){
      Qmat[j-1,i]=1
    }else if(qval<0){
      Qmat[j-1,i]=-1
    }
  }
}
K=sum(Qmat)
tauhat=K/(n*(n-1)/2)
tauhat
```


Problem 8.28
```{r}
require(NSM3)
kendall.ci(x,y, alpha = 0.1)
```

Problem 8.3 - Spearman Method
H0: η=0 
H1: η=/0
From our results, we see that our p-value is greater 0.1 
Therefore, we do not reject the null hypothesis that brain weight and large fiber count are independent 
Comparing this to Kendall's we see that both methods did not reject the null hypothesis, but Spearman's Method gave a smaller p-value 
```{r}
cor.test(x,y, method = "spearman")
```


Problem 8.22 - Spearman Method
Seeing the previous output, we see that our rho = 0.427. So rho is greater than tau that was solved for Kendall's 


Problem 8.28 - Spearnman Method
Our 90% confidence interval is from -0.2165899 to 0.8100000, comparing this to Kendall's Spearman Method has a wider confidence interval 
```{r}
require(RVAideMemoire)
spearman.ci(data8.4$weight,data8.4$count,conf.level=0.9)
```





