---
title: "Homework 2"
author: "Jong Hyun Choi"
date: '2021 2 14 '
output:
  word_document: default
  html_document: default
---
```{r}
data3.3 = read.csv("tab3_3.csv")
data4.3 = read.csv("tab4_3.csv")
```
Exercise 1 
3.3 





3.6 
The smallest possible value for T+ would be 0 if there are no Zi values that are greater than 0. The greatest possible value for T+ would be n(n+1)/2 - T- where T- could be 0 if all Zi > 0. 


Exercise 2 
The null hypothesis: Ho:theta =theta0 
alternative hypothesis: H1: theta > theta0 
Because we set alpha = 0.1, we see that our p-value is less than our alpha. So we reject our null hypothesis. 
Our estimate median is 80 and our confidence interval is from 15 to infinity
```{r}
wilcox.test(data3.3$y - data3.3$x, alternative = "greater", conf.level = 0.9)
require(NSM3)
owa(data3.3$x, data3.3$y)
wilcox.test(data3.3$y - data3.3$x, alternative = "greater", conf.int = TRUE, conf.level = 0.9)
```

Exercise 3 
Without assuming symmetry,
the null hypothesis: Ho: theta = theta0
alternative hypothesis: H1: theta > theta0
We do reject the null hypothesis with p-value less than alpha which is 0.1
But our confidence interval is 12.3 to infinity which is lower than exercise 2,and the estimate median is also lower

```{r}
require(BSDA)
SIGN.test(data3.3$y, data3.3$x, alternative = "greater", conf.level = 0.9, conf.int = TRUE)
median(data3.3$y - data3.3$x)
```
4.2 
We know that W = 30 
We know that W' is sum of ranks of the X observations. And we see if we add W and W', we get 120 and we can verify this using W +W' = ((m+n)(m+n+1)/2
```{r}
1+3+4+7+10+11+12+13+14+15
30+90
```

Since m corresponds to number of observations in X and n corresponds to number of observations in Y, we see that m = 10 and n=5 
```{r}
((10+5)*(10+5+1))/2
```

4.4
We are given the equation U'+U = mn
we know U = 15 to find U' we can use wilcox.test, and see that U' = 35
```{r}
at.term<−c (.80, .83, 1.89, 1.04, 1.45, 1.38, 1.91, 1.64, .73, 1.46)
gest.age<−c (1.15, .88, .90, .74, 1.21)
wilcox.test(at.term, gest.age, alternative = "t")
```
since m = 10 and n = 5, we have validated the equation
```{r}
10*5
15+35
```


Exercise 5 
```{r}
x = data4.3$nonallergics
y = data4.3$allergics
```
Null hypothesis: Ho:delta = 0 
alternative hypotehsis: H1: delta > 0 
```{r}
wilcox.test(y,x, alternative = "greater", conf.int = TRUE, conf.level = 0.99)
```

We see that our p-value is less than our alpha =0.1 so we reject the null hypothesis.
Our confidence interval is 25.9 to infinity and our estimate of the location shift is 54.3

Using large sample approximation, 
our expected value: 
```{r}
exp=(9*(13+9+1))/2
```

variance:
```{r}
var=(9*13*(13+9+1))/12
```

sum of ranks assigned to Y-values 
```{r}
W=7+11+16+17+18+19+20+21+22
```

```{r}
Wstar= (W-exp)/((var)^(1/2))
```
Because 3.17 is greater than our z-score of 0.01 significance level, which is 2.58 we reject the null hypothesis. 


