---
title: "Homework 6"
author: "Jong Hyun Choi"
date: "5/2/2021"
output:
  word_document: default
  html_document: default
---

Exercise 1:
a~f) 
```{r}
data(mtcars)
plot(mtcars$hp, mtcars$mpg, xlab= "car's horsepower", ylab= "miles per gallon")
abline(lm(mtcars$mpg~ mtcars$hp))
locavg = with(mtcars, supsmu(hp, mpg))
lines(locavg, col = "green")
locreg <- with(mtcars, loess(mpg~hp))
j=order(mtcars$hp)
lines(mtcars$hp[j], locreg$fitted[j], col = "red")

loess.gcv <- function(x, y){
  nobs <- length(y)
  xs <- sort(x, index.return = TRUE)
  x <- xs$x
  y <- y[xs$ix]
  tune.loess <- function(s){
    lo <- loess(y ~ x, span = s)
    mean((lo$fitted - y)^2) / (1 - lo$trace.hat/nobs)^2
  }
  os <- optimize(tune.loess, interval = c(.01, 99))$minimum
  lo <- loess(y ~ x, span = os)
  list(x = x, y = lo$fitted, df = lo$trace.hat, span = os)
}
locreg = with(mtcars, loess.gcv(hp, mpg))
lines(locreg, col = "blue")

fit <- ksmooth(mtcars$hp, mtcars$mpg, bandwidth = 0.5)
lines(fit, col= "orange")


ksmooth.gcv <- function(x, y){
  nobs <- length(y)
  xs <- sort(x, index.return = TRUE)
  x <- xs$x
  y <- y[xs$ix]
  xdif <- outer(x, x, FUN = "-")
  tune.ksmooth <- function(h){
    xden <- dnorm(xdif / h)
    xden <- xden / rowSums(xden)
    df <- sum(diag(xden))
    fit <- xden %*% y
    mean((fit - y)^2) / (1 - df/nobs)^2
  }
  xrng <- diff(range(x))
  oh <- optimize(tune.ksmooth, interval = c(xrng/nobs, xrng))$minimum
  if(any(oh == c(xrng/nobs, xrng)))
    warning("Minimum found on boundary of search range.\nYou should retune model with expanded range.")
  xden <- dnorm(xdif / oh)
  xden <- xden / rowSums(xden)
  df <- sum(diag(xden))
  fit <- xden %*% y
  list(x = x, y = fit, df = df, h = oh)
}
kern <- with(mtcars, ksmooth.gcv(mtcars$hp, mtcars$mpg))
lines(kern, col = "cyan")
```

g) The similarities between the approaches is that most of the graphs are pretty smooth and they all follow the same path. However, the only difference is that the green and the cyan colored lines are more jagged than the others 

Exercise 2 
```{r}
library(npreg)
```

a) 
```{r}
mod.ss <- with(mtcars, ss(hp, mpg))
plot(mod.ss, xlab= "car's horsepower", ylab= "miles per gallon")
points(mtcars$hp, mtcars$mpg)
```

b) 
```{r}
mod.ss <- with(mtcars, ss(hp, mpg, method = "OCV"))
plot(mod.ss, xlab= "car's horsepower", ylab= "miles per gallon")
points(mtcars$hp, mtcars$mpg)
```

c) 
```{r}
mod.ss <- with(mtcars, ss(hp, mpg, method = "REML"))
plot(mod.ss, xlab= "car's horsepower", ylab= "miles per gallon")
points(mtcars$hp, mtcars$mpg)
```

d) 
```{r}
mod.ss <- with(mtcars, ss(hp, mpg, nknots =10))
plot(mod.ss, xlab= "car's horsepower", ylab= "miles per gallon")
points(mtcars$hp, mtcars$mpg)
```

e) 
```{r}
mod.ss <- with(mtcars, ss(hp, mpg, method = "OCV", nknots = 10))
plot(mod.ss, xlab= "car's horsepower", ylab= "miles per gallon")
points(mtcars$hp, mtcars$mpg)
```
f) 
```{r}
mod.ss <- with(mtcars, ss(hp, mpg, method = "REML", nknots = 10))
plot(mod.ss, xlab= "car's horsepower", ylab= "miles per gallon")
points(mtcars$hp, mtcars$mpg)
```

g) The similarities is that the graphs from part b to f have almost identical graphs. Also, the df for all the graphs except for part a is around 4. The only difference is that the graph in part a has totally different looking shaped graph and the df is around 21. 




